A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-09-29 paper.tex
Minor fixes

\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{float}
\usepackage{tabularx}
\usepackage{makecell}
\usepackage{multirow}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic,algorithm}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\usepackage[T1]{fontenc}
\graphicspath{{./images/}}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\author{\IEEEauthorblockN{Ching-Hua (Vivian) Lin}
\IEEEauthorblockA{dept. of CSIE\\
National Cheng Kung University\\
Tainan City, Taiwan (R.O.C.)\\
jkrvivian@gmail.com}
\and
\IEEEauthorblockN{Ching-Chun (Jim) Huang}
\IEEEauthorblockA{dept. of CSIE\\
National Cheng Kung University\\
Tainan City, Taiwan (R.O.C.)\\
jserv@ccns.ncku.edu.tw}
\and
\IEEEauthorblockN{Yang-Hao Yuan}
\IEEEauthorblockA{BiiLabs Co., Ltd.\\
Taiwan (R.O.C.)\\
<yanghau@biilabs.io>}
\and
\IEEEauthorblockN{Zih-shiuan (Spin) Yuan}
\IEEEauthorblockA{BiiLabs Co., Ltd.\\
Taiwan (R.O.C.)\\
<spin@biilabs.io>}
}

@@

\begin{abstract}
%cite IoT data subscription economy
On top of subscription-based pricing models such as Software-as-a-Service (SaaS), monetizing the subscription enables the payment of data streams with data usage instead of a particular price for a fixed data set. This pricing model allows data providers to have a better vision of managing budgets and data consumers to have the flexibility to subscribe and unsubscribe. However, unlike static data collections, the streaming data increases difficulties of dynamic data ownership and identity verification. A trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any service or participants. In addition, an automated subscription procedure is also demanded for the sake of data monetization. In this paper, we leverage usages of distributed ledger technologies (DLTs) to construct a decentralized data trading platform on top of the IoT brokered infrastructure. This approach can efficiently enhance the degree of transparency and scalability. The storage built upon cryptographic message protocols allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the digital rights of trading participants deserve a guarantee, which is enabled by design.
\end{abstract}

@@

%publish/subscribe 的機制符合 IoT 應用情境，因為只在意部份資料
In contrast to the existing solutions targeting static data sets\cite{DIaas, MARSA}, this paper aims for processing the high volume, high velocity, and high variety of real-time data streams\cite{BigData}. As streaming data is composed of records at every moment, users or devices are interested in data of a specific time period instead of the whole timeline. For example, the Internet of Vehicles (IoV) allows vehicles to connect with traffic signs and bicycles, share information, and at the same time be able to understand the real-time environmental conditions and find the best route through the communication. While vehicles and traffic lights continuously generate information, a device only needs to process the data streams of surroundings but all appliances in the IoV.

%trustless & automated
%trust: 對系統、對身份、對資料
In data trading platforms, there are three major aspects that need trust: identity, data ownership, and trading.
Among the challenges of data trading platform\cite{BigDataMarket}, the following characteristics are required:
\begin{itemize}
    \item \textbf{Scalability}.
1) The performance of the platform should scale with the massive amount of participants. 2) The keys and entry points of data products managed by participants should be as small as possible.
    \item \textbf{Integrity}. 1) Prevent unauthorized modifications. 2) Ensure the accuracy and validity of contents.
    \item \textbf{Confidentiality}.
1) Only the authorized participants can access data streams. 2) Participants that have access can always retrieve data even if they're dropped from the network.
    \item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leak within the subscription history.
\end{itemize}

@@

%pic
\begin{figure}[!h]
    \centering
    \includegraphics[width=3in]{MAM_E2EE_fold}
    \caption{The process of E2EE.}
    \label{fig:MAM_E2EE}
\end{figure}

>>>>

\usepackage{cite}
\usepackage{float}
\usepackage{tabularx}
\usepackage{makecell}
\usepackage{multirow}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic,algorithm}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\usepackage[T1]{fontenc}
\graphicspath{{./images/}}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\author{\IEEEauthorblockN{Ching-Hua (Vivian) Lin}
\IEEEauthorblockA{dept. of CSIE\\
National Cheng Kung University\\
Tainan City, Taiwan (R.O.C.)\\
jkrvivian@gmail.com}
\and
\IEEEauthorblockN{Ching-Chun (Jim) Huang}
\IEEEauthorblockA{dept. of CSIE\\
National Cheng Kung University\\
Tainan City, Taiwan (R.O.C.)\\
jserv@ccns.ncku.edu.tw}
\and
\IEEEauthorblockN{Yang-Hao Yuan}
\IEEEauthorblockA{BiiLabs Co., Ltd.\\
Taiwan (R.O.C.)\\
yanghau@biilabs.io}
\and
\IEEEauthorblockN{Zih-shiuan (Spin) Yuan}
\IEEEauthorblockA{BiiLabs Co., Ltd.\\
Taiwan (R.O.C.)\\
spin@biilabs.io}
}

@@

\begin{abstract}
On top of subscription-based pricing models such as Software-as-a-Service (SaaS), monetizing the subscription enables the payment of data streams with data usage instead of a particular price for a fixed data set. This pricing model allows data providers to have a better vision of managing budgets and data consumers to have the flexibility to subscribe and unsubscribe. However, unlike static data collections, the streaming data increases difficulties of dynamic data ownership and identity verification. A trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any service or participants. In addition, an automated subscription procedure is also demanded for the sake of data monetization. In this paper, we leverage usages of distributed ledger technologies (DLTs) to construct a decentralized data trading platform on top of the IoT brokered infrastructure. This approach can efficiently enhance the degree of transparency and scalability. The storage built upon cryptographic message protocols allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the digital rights of trading participants deserve a guarantee, which is enabled by design.
\end{abstract}

@@

In contrast to the existing solutions targeting static data sets\cite{DIaas, MARSA}, this paper aims for processing the high volume, high velocity, and high variety of real-time data streams\cite{BigData}. As streaming data is composed of records at every moment, users or devices are interested in data of a specific time period instead of the whole timeline. For example, the Internet of Vehicles (IoV) allows vehicles to connect with traffic signs and bicycles, share information, and at the same time be able to understand the real-time environmental conditions and find the best route through the communication. While vehicles and traffic lights continuously generate information, a device only needs to process the data streams of surroundings but all appliances in the IoV.

In data trading platforms, there are three major aspects that need trust: identity, data ownership, and trading.
Among the challenges of data trading platform\cite{BigDataMarket}, the following characteristics are required:
\begin{itemize}
    \item \textbf{Scalability}.
1) The performance of the platform should scale with the massive amount of participants. 2) The keys and entry points of data products managed by participants should be as small as possible.
    \item \textbf{Integrity}. 1) Prevent unauthorized modifications. 2) Ensure the accuracy and validity of contents.
    \item \textbf{Confidentiality}.
1) Only the authorized participants can access data streams. 2) Participants that have access can always retrieve data even if they're dropped from the network.
    \item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leak within the subscription history.
\end{itemize}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=3in]{MAM_E2EE_fold}
    \caption{The process of E2EE.}
    \label{fig:MAM_E2EE}
\end{figure}
